\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix A -- Original Results} }

### 2018-12-02 Final Paper/PaperJLin.tex
Fixed up tables

\begin{figure}[ht!]    \centering
	{	 \includegraphics[width=\textwidth]{DemAge}}
	\caption{\tb{Level of Democracy and Regime Age}}\label{figure2}
\end{figure}

@@

@@

@@

@@

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&-.1005*** \\
		&(.0136)\\
		Suburban&-.1737***\\
		&(.0162) \\
		Urban&-.1306*** \\
		&(.0123)\\
		Constant&5.7164*** \\
		&(.0093) \\
		N&42,500 \\
		$R^2$&0.0037 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &-.1000***&-.0018 \\
	&(.0339)&(.0130) \\
	Suburban& -.1517***& .0147 \\
	&(.0401)& (.0157) \\
	Urban&-.0517* & -.0420*** \\
	&(.0304) & (.0117) \\
	\e{Democracy}& -.1995*** & -.0421***\\
	&(.0110) & (.0040)\\
	\e{Regime Age} & -.0014*** &  -.0075***\\
	&(.0002) & (.0001)\\
	\e{Electoral Formula}&.0778*** & -.0440***\\
	&(.0189) & (.0070) \\
	\hline
	Constant& 7.3627*** & 6.5149*** \\
	&(.1067) & (.0391)\\
	N&46,555 & 41,373 \\
	$R^2$&0.0135& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[h!]
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Variables Used in Analyses}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Variable Name}& \tb{Variable Number} & \tb{Description}&\tb{Outside Source} \\
		\hline
		Election ID Variable &D1004&Polity and Election Year&-\\
		Place of Residence&D2031&Rural or Urban Residence&-\\
		Left-Right Self&D3014&Self-rate ideology &-\\
		Level of Democracy&D5051\_1&Democracy-Autocracy at Election&Polity IV Project\\
		Age of Current Regime&D5052&Age of Regime in Years& Polity IV Project\\
		Electoral Formula&D5058&Method of Election&CSES Macro Report\\
		\hline
	\end{tabulary}\\
	\e{Source:} Comparative Study of Electoral Systems Module IV Codebook available at \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}
	\label{table99}
\end{table}

@@

The \txt{liberalism} variable was generate by an aggregation of the 9 questions. Each of the variables were recoded and summed. The final score yielded a 0-9 scale where a person who scored a 9 is evaluated as the most liberal in terms of their view on economic and social policy, whereas someone with a score of 0 would be the most opposite.

>>>>

\begin{figure}[ht!]    \centering
	{	 \includegraphics[width=\textwidth]{RegimeDemocracy}}
	\caption{\tb{Level of Democracy and Regime Age}}\label{figure2}
\end{figure}

@@

To ensure that we are able to compare the countries and individuals purely based on the place of residence, I employ several controls to the model. These include gender, highest level of education, socioeconomic status, age of respondent, religiosity of respondent, party identification and closeness to a party.

The gender of the respondent is a dichotomous scale of male versus female. Subjects have the opportunity to decline to respond, as they do in all other variables. Education measures the highest level of education attained by the respondent. The socioeconomic status (SES) measures where the respondent stands on the income ladder. A respondent's age is coded based on the year this analysis is conducted (2018) subtracted from their birth year.

Religiosity is included as a control because it is often the case that more religious individuals tend to be more conservative. Therefore, this variable measures the extent to which the respondent would agree that they are religious, not necessarily which denomination they identify with.

Party identification varies widely by country, especially based on the way it is coded in the CSES. Therefore, party ID is treated as a control in the general analysis, along with an individual's feelings of closeness to the party.

As a result of employing these controls, the number of respondents that we can study drastically decreases from the number of available samples in the original dataset. This is because, as mentioned earlier, any respondent who refuses or does not know the answer is marked as missing data. While this method allows us to get a better picture of the relationship between place and political ideology, it systematically rules out certain countries from the picture because of non-response or lack of inclusion of a particular item in the country's version of the questionnaire

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Worldwide} \\
			\hline
			Small Town&-.1338***  \\    
			& (.0336)   \\
			Suburban & -.2591***\\ 
			& (.0358) \\
			Urban   & -.0482   \\
			& (.0300)    \\
			Constant   & 5.597***  \\
			&(.0234) \\
			N  & 47,821  \\
			$R^2$	& 0.0011 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table3}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central/Latin America}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
			\hline
			Small Town  & .8064   &-1.428***    & -   \\      
			 & (1.317) & (.5255)    & -    \\
			Suburban     & -   & -   & -    \\ 
			  & -    & -   & -    \\
			Urban    & 1.107  & -1.2411***   & .2059  \\
			  &(1.1060)   & (.3994)  & (.4962)      \\
			Constant  & 12.697*** & 7.306*** & 6.820***  \\
			&(2.073)&(1.008)&(1.390) \\
			N   &96   & 327 & 267   \\
			$R^2$ & 0.2811   &0.0695   &0.0557     \\
			\hline                   
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table4}
	\end{table}
\end{singlespace}

\begin{singlespace}
\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town   & -.0753 &-.1266  \\      
			& (.2080)  & (.1680)   \\
			Suburban   & .2526 & -.0432    \\ 
			 & (.3290)  & (.2310)    \\
			Urban   & -.2544 & -.6460***    \\
			 &(.2490)  & (.1706)   \\
			Constant  & 5.399***  & 1.3237** \\
			&(0.0845)&(.6009) \\
			N  &427  & 1,332    \\
			$R^2$  &0.1072 &0.0866  \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table5}
\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town&.2546&1.131***&-.0247 \\
			&(.4143)&(.4036)&(.4636) \\
			Suburban&.0600&1.866***&.0325 \\
			&(.3463)&(.4081)&(.4431) \\
			Urban&-.6608&.9035**& .0217\\
			&(.4514)&(.3993)&(.4006) \\
			Constant&6.5998***&6.063***&2.352** \\
			&(1.123)&(.8182)&(1.116) \\
			N&187&428&330\\
			$R^2$&0.2158&0.1688&0.0677 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table6}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c c}
			\\
			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia} \\
			\hline
			Small Town&.6270**& -.1272 & .3032 & .3954  \\
			&(.3139) & (.2920) & (.2002) & (.3216) \\
			Suburban&-.0326& -.4467&.0666 & 2.1723\\
			&(.3343)&(.4993) & (.3104) & (.1.107)\\
			Urban&.3822&.5199 & .0954 & 1.1440 \\
			&(.3888) &(.2944) & (.2662) & (.4518) \\
			Constant& 4.014***& 3.930***& 5.096*** & 4.3473***  \\
			&(.9272) & (.8696) & (.8646) & (1.127) \\
			N&247& 511& 895 & 392 \\
			$R^2$&0.1126&0.2538 & 0.1348 & 0.1498 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table7}
	\end{table}
\end{singlespace}

%Southwestern Europe

@@

%Fixed to include Controls
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&.0432 \\
		&(.0278)\\
		Suburban&.0082\\
		&(.0352) \\
		Urban&.0995*** \\
		&(.0272)\\
		Constant&2.7915*** \\
		&(.0762) \\
		N&9.662 \\
		$R^2$&0.0195 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

%Self Placement Column Changed
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &.0231&-.0018 \\
	&(.0519)&(.0130) \\
	Suburban& .0555***& .0147 \\
	&(.0688)& (.0157) \\
	Urban&.1214** & -.0420*** \\
	&(.0507) & (.0117) \\
	\e{Democracy}& -.1599*** & -.0421***\\
	&(.0190) & (.0040)\\
	\e{Regime Age} & .0013 &  -.0075***\\
	&(.00027) & (.0001)\\
	\e{Electoral Formula}&.0789*** & -.0440***\\
	&(.0302) & (.0070) \\
	\hline
	Constant& 6.510*** & 6.5149*** \\
	&(.2067) & (.0391)\\
	N&18748 & 41,373 \\
	$R^2$&0.0406& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Variables Used in Analyses}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Variable Name}& \tb{Variable Number} & \tb{Description}&\tb{Outside Source} \\
		\hline
		Election ID Variable &D1004&Polity and Election Year&-\\
		Place of Residence&D2031&Rural or Urban Residence&-\\
		Left-Right Self&D3014&Self-rate ideology &-\\
		Age&D2001\_Y&2018-VAR-Value&- \\
		Gender&D2002&Gender of Respondent&- \\
		Education&D2003&Highest Education Attained&- \\
		Socioeconomic Status&D2012&SES&- \\
		Religiosity&D2025&Identifies with religion?&-  \\
		Party ID&D3018\_3&Party Closest to R&- \\
		Closeness&D3018\_4&Party attachment&- \\
		Level of Democracy&D5051\_1&Democracy-Autocracy at Election&Polity IV Project\\
		Age of Current Regime&D5052&Age of Regime in Years& Polity IV Project\\
		Electoral Formula&D5058&Method of Election&CSES Macro Report\\
		\hline
	\end{tabulary}\\
	\e{Source:} Comparative Study of Electoral Systems Module IV Codebook available at \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}
	\label{table99}
\end{table}

@@

The \txt{liberalism} variable was generate by an aggregation of the 9 questions. Each of the variables were recoded and summed. The final score yielded a 0-9 scale where a person who scored a 9 is evaluated as the most conservative in terms of their view on economic and social policy, whereas someone with a score of 0 would be the most opposite.

### 2018-12-02 Online Appendices/Appendix A.tex
Fixed up tables

>>>>

\section{General Trends For Both Objective Issue Stances and Self-Placement Ideology}

\begin{singlespace}
	\begin{table}[H]
		\centering
		\def\arraystretch{1}
		\caption{\tb{General Trends of Ideology}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Self-Placement} & \tb{Liberalism} \\
			\hline
			Small Town&-.1338***& -.1005*** \\    
			& (.0336) & (.0136)  \\
			Suburban & -.2591*** &-.1737 ***\\ 
			& (.0358) &(.0162) \\
			Urban   & -.0482 &-.1309***  \\
			& (.0300)  &(.123)  \\
			Constant   & 5.597*** &5.7164*** \\
			&(.0234) & (.0093)\\
			N  & 47,821 & 42,500 \\
			$R^2$	& 0.0011 & 0.0037 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table102}
	\end{table}
\end{singlespace}

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
		\hline
		\e{Place of Residence} & & \\
		Small Town &-.1000***&-.0018 \\
		&(.0339)&(.0130) \\
		Suburban& -.1517***& .0147 \\
		&(.0401)& (.0157) \\
		Urban&-.0517* & -.0420*** \\
		&(.0304) & (.0117) \\
		\e{Democracy}& -.1995*** & -.0421***\\
		&(.0110) & (.0040)\\
		\e{Regime Age} & -.0014*** &  -.0075***\\
		&(.0002) & (.0001)\\
		\e{Electoral Formula}&.0778*** & -.0440***\\
		&(.0189) & (.0070) \\
		\hline
		Constant& 7.3627*** & 6.5149*** \\
		&(.1067) & (.0391)\\
		N&46,555 & 41,373 \\
		$R^2$&0.0135& 0.1273 \\
		\hline
	\end{tabulary}
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table15}
\end{table}

\begin{table}[h!]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.6640*** &.0608 &-.1600** \\
		&(.0766)&(.0435) &(.0727) \\
		Suburban&-.6389*** &-.1894***&-.1260  \\
		&(.1042) &(.0451) &(.1180) \\
		Urban&-.5781*** &-.0327 &.2655*** \\
		&(.0710) &(.0388) &(.0644) \\
		Constant& 5.8256*** &5.5408***&5.5562*** \\
		&(.0543) &(.0297) &(.0531) \\
		Countries&5&21&6 \\
		N&8,350&28,869 &10,602 \\
		$R^2$&0.0114&0.0011 &0.0052 \\
		\hline 
	\end{tabulary} 
	\\ 
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table16}
\end{table}
